The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-05-20 paper/ms.tex
zenodo citation

All smear light curves in this paper, as well as the \LaTeX{} source code used to produce this document, can be found
at \href{https://github.com/benjaminpope/smearcampaign}{\nolinkurl{github.com/benjaminpope/smearcampaign}}.

>>>>

All smear light curves in this paper, as well as the \LaTeX{} source code used to produce this document, can be found
at \href{https://github.com/benjaminpope/smearcampaign}{\nolinkurl{github.com/benjaminpope/smearcampaign}}\footnote{\dataset[10.5281/zenodo.3066218]{\doi{10.5281/zenodo.3066218}} \citep{smearcampaign_zenodo}}.
